Selectively Remove Variables

### 2022-11-14 src/Selectively_remove_variables.Rmd

```{r}
library(knitr)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(stats)
library(tidyverse)
library(e1071)
library(car)
```

```{r}
countries <- read.csv("../data/countries.csv")
```

@@

#subset1 <- subset(countries, select = c("edu.total", "fdi", "gcf", "gdp.dflt", "hlth", "income", "lbr.part", "mil", "pop.gwth rural", "pop.gwth.urban", "pov", "reg", "trade", "unemp", "year"))
subset0 <- subset(countries, select = c("edu.total", "fdi","gcf","gdp.dflt","hlth","income","lbr.part","mil","pop.gwth.rural","pop.gwth.urban","pov","trade", "unemp", "year","gdp.pc" ))

subset1 <- subset0 %>% mutate(lfdi = log(subset1$fdi)) %>% mutate(lgdp.pc = log(subset1$gdp.pc)) %>% mutate(lgdp.gdlt = log(subset1$gdp.dflt))
#dataset
```

@@

```
Constant varince assumption not satisfied. What to do? Most likely need to transform the variable

@@

>>>>

```{r}
library(knitr)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(stats)
library(tidyverse)
library(e1071)
library(car)
library(glmnet)
library(corrplot)
```
We first read the 
```{r}
countries <- read.csv("../data/countries.csv")
```

@@

#subset1 <- subset(countries, select = c("edu.total", "fdi", "gcf", "gdp.dflt", "hlth", "income", "lbr.part", "mil", "pop.gwth.rural", "pop.gwth.urban", "pov", "reg", "trade", "unemp", "year"))
subset0 <- subset(countries, select = c("edu.total", "fdi","gcf","gdp.dflt","hlth","income","lbr.part","mil","pop.gwth.rural","pop.gwth.urban","pov","trade", "unemp", "year","gdp.pc" ))

subset1 <- subset0 %>% mutate(lfdi = log(subset0$fdi)) %>% mutate(lgdp.pc = log(subset0$gdp.pc)) %>% mutate(lgdp.gdlt = log(subset0$gdp.dflt))
#dataset
```

@@

```
Constant varince assumption not satisfied. What to do? Most likely need to transform the variable
TO TRANSFORM TO BOXCOX

@@

```{r}
#Train a LASSO regression model
set.seed(123)
cv_lasso <- cv.glmnet(train.x, train.y, alpha = 1, type.measure = "mse")
```

```{r}
cv_lasso
```

```{r}
plot(cv_lasso)
```

```{r}
glm_Lasso <- glmnet(train.x, train.y, alpha = 1, lambda = cv_lasso$lambda.min)
t(coef(glm_Lasso))
```

```{r}
fit2 <- predict(glm_Lasso, train.x)
true2 <- train.y
summary_Lasso_train <- eval_results(fit2, true2)
summary_Lasso_train
```

```{r}
fit3 <- predict(glm_Lasso, test.x)
true3 <- test.y
summary_Lasso_test <- eval_results(fit3, true3)
summary_Lasso_test
```
